ramipril cough amlodipine (by ArticleAggregator_v05)

### 2023-02-21 ArticleAggregatorCS.qmd
Final egp_v01.xlsx downloaded

## Procedure
- EMBASE search: Zentiva Network or VPN, search in "Title, Abstract or Author Keywords"
- Export result in Excel Column Format with following fields: 
    1. Title
    2. Author names
    3. Publication Year
    4. Publication type
    5. Date of publication
    6. Digital Object Identifier (DOI)
    7. Medline PMID
    8. Embase identification number (PUI)
    9. Abstract
    10. Clinical Trial Number
    11. Full text link
    12. Embase link
    13. Open URL Link
- Save to working directory as "eb_src.xlsx"
- Install packages
- Load packages
- Set environment check "term" and "aa_path"
- Decide if use Scholar only for in titles search or full search (enable corresponding url)
-

>>>>

## Procedure
- EMBASE search: Zentiva Network or VPN, search in "Title, Abstract or Author Keywords"
- Export result in Excel Column Format with following fields: 
    1. Title
    2. Author names
    3. Publication Year
    4. Publication type
    5. Date of publication
    6. Digital Object Identifier (DOI)
    7. Medline PMID
    8. Embase identification number (PUI)
    9. Abstract
    10. Clinical Trial Number
    11. Full text link
    12. Embase link
    13. Open URL Link
- Save to working directory as "eb_src.xlsx"
- Install packages
- Load packages
- Set environment check "term" and "aa_path"
- Decide if use Scholar only for in titles search or full search (enable corresponding url)
- Final Excel table as "egp_v01.xlsx"
